---
title       : Estimating MPG for Cars
subtitle    : Shiny Application 
author      : Yetik Serbest
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : [bootstrap, quiz, shiny, interactive]            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---

## Tool Description

- It calculates MPG estimate for a car given the following information
  * Transmission type
  * Number of Cylinders in the engine
  * Weight of the car
  * Horse power of the car
- The calculation is done based on the linear model developed using mtcars data set in R
- User enters the parameters as well as the confidence interval
- The tool provides the estimated MPG, confidence interval, and the plot for the confidence interval
- The tool is hosted in this link [here] (https://yetikserbest.shinyapps.io/DevelopingDataProductsProject/)

--- .class #id 

## Tool Layout

* The tool has an input panel
* The tool has two output tabs: 1. Result, 2. Plot
* Result tab provide the estimated MPG and the confidence limits
* Plot tab provides the diagram for the confidence interval
* By default, the tool displays ui.R and server.R files on the right
* By default, the tool displays the tool readme file at the bottom

---

## MPG Calculation Detail

- Shiny application is a wrapper to make it easy for the user and the user does not need to know R
- This is the exact model used in the application

```{r }
data(mtcars)
fit <- lm(mpg ~ factor(am) + wt + factor(cyl) + hp, data=mtcars)

```

- The follwing is an example calculation

```{r}
predict(fit,newdata=list(am=factor(1),wt=3,cyl=factor(6),hp=280),interval=("confidence"), level=0.95)

```


--- &interactive

## Tool Interactive Console

```{r opts.label = 'shiny'}
  slidifyUI(
    radioButtons("transmission","Transmission Type:",
                 list("Automatic"="0","Manual"="1")),
    radioButtons("cylinder","Number of Cylinders:",
                 list("4 Cylinders"="4","6 Cylinders"="6","8 Cylinders"="8")),
    textInput(inputId="weight",label="Weight of the car (in 1000lb)"),
    textInput(inputId="horsepower",label="Horse Power of the car"),
    sliderInput("confint","Confidence Interval:",0,1,0.05),
    submitButton('Submit')
  )
  mainPanel(
#    textOutput('result')
    tags$div(id = 'nvd3plot', class='shiny-html-output nvd3 rChart')
)

```
